Adopting agile software development in the large organizations: A systematic literature review

### 2014-05-31 journal/article.tex
T: External consultants: Work in progress

Agile methods have become an appealing alternative for companies striving to
improve their performance, but the methods are originally designed for small and
individual teams. This poses challenges when introducing agile to large
organizations where development teams can not be autonomous. We reviewed 30
experience reports and case studies describing the process of taking agile
methods into use in large organizations. The primary motive for agile adoption
is the need to improve performance. For a successful transformation the entire
organization must be aligned and all organizational units must participate.
Creating an agile community in the organization will help the change to stick.
Typical problems are misunderstanding of the agile model, and difficulties
coordinating multiple agile teams.

@@

% Why
Coaching was considered necessary, especially in the beginning of agile projects
[P6, P8, P33, P46, 47]. Brown [P8] stated that without adequate coaching there
would have been severe long term consequences [P8]. The application of coaching
was seen as an important success factor [P29, P33], and the job of the coach was
described to be to ensure that the transformation would be successful [P16].
One viewpoint was that the coach was an impartial third party who could be
relied on when resolving transformation impediments [P29].

@@

% How coaching evolves
As the agile way of working penetrated the organization the need for coaching
was decreasing, and coaching could be reduced [P18, P36]. However, some cases
described that the demand for coaching had become permanent in order to keep the
development model healthy and to continuously pursue improvement [P6, P23].
The maturity of coaches was described to grow over time, as the agile
transformation progressed [P32].

@@

@@

@@

@@

\begin{table}[h]
    \centering
    \begin{tabular}{ >{\raggedright\arraybackslash}p{0.51\textwidth}
                     >{\raggedright\arraybackslash}p{0.41\textwidth} }
        \toprule
        Success factors  &  Described in \\
        \midrule
        Training is necessary to achieve change  &
                P3, P6, P11, P14, P16, P30, P37, P46 \\
        Coaching is essential in transformation  &
                P3, P6, P8, P9 P16, P17, P18, P30, P42, P44, P47, P48  \\
        \bottomrule
    \end{tabular}
    \caption{XXXXXXXXXXXXXX}
    \label{table:success_NN}
\end{table}

@@

Agile methods avoid prescribing exact ways of working but rather emphasize a
mindset of adapting to the situation. It is difficult to explain by theory how
such a mindset should be applied, and the agile practices are best learned by
doing. Coaching teams while they apply the agile methods in practice was seen as
an important factor in change [P3, P16, P17, P30, P47]. A few cases stated even
that coaching was essential for success in transformation [P8, P18]. Also,
without coaching teams can do damage to the agile transformation if techniques
are applied improperly [P9].

@@

>>>>

Agile methods have become an appealing alternative for companies striving to
improve their performance, but the methods are originally designed for small and
individual teams. This creates unique challenges when introducing agile to large
organizations where development teams can not be autonomous. We conducted a
systematic literature review including publications on 40 industry cases,
describing the process of taking agile methods into use in large organizations.

The primary motive for agile adoption is the need to improve performance. For a
successful transformation the entire organization must be aligned and all
organizational units must participate.
Creating an agile community in the organization will help the change to stick.
Typical problems are misunderstanding of the agile model, and difficulties
coordinating multiple agile teams.

@@

% Why
Coaching was considered necessary, especially in the beginning of agile projects
[P6, P8, P33, P46, 47]. Brown [P8] stated that without adequate coaching there
would have been severe long term consequences [P8]. The application of coaching
was seen as an important success factor [P18, P29, P33], and the job of the
coach was described to be to ensure that the transformation would be successful
[P16]. One viewpoint was that the coach was an impartial third party who could
be relied on when resolving transformation impediments [P16, P29, P44].

@@

% How coaching evolves
As the agile way of working penetrated the organization the need for coaching
was decreasing, and coaching could be reduced [P18, P36]. However, some cases
described that the demand for coaching had become permanent in order to keep the
development model healthy and to continuously pursue improvement [P6, P23].
External coaches moved out and internal coaches took their place [P40].
The maturity of coaches was described to grow over time, as the agile
transformation progressed [P32].

@@

% External consultants

Who are they?

Why are they hired?

When in the transformation?

What did they do?

Benefit was what?

@@

External consultants were employed especially at the start of the
transformation. At the time it was realized that the organization should change
the way of working a consultant was typically hired to give an introduction to
agile.

It was described that external consultants were invited every now and then to
bring in fresh ideas to the organization [P6].

External consultants were especially used in the beginning to ignite interest in
agile methods [P9].

External consultants assessed the current state of the organization, and
recommended what kind of model to apply [P51].

It was recommended to bring in extenal help as early as possible, before truoble
starts rising in the transformation [P16].

People were also more comfortable when the advice was given by impartial persons
external to the organization [P16, P29].

A particular wish in using consultants was that they would speed up the adoption
[P34]. Consultants were already experts in the agile methods and could quickly
tell solutions to problems.

@@

[P5]
* Who: Dean Leffingwell
* What: Advise, and tell to do what's next

[P6]
* When: Pilot teams
* Who: Ken Schwaber, etc.
* What: Early coaching
--
* What: Coach Scrum masters
* When: Continue inviting agile experts
* What: Bring fresh ideas
--
* Why: It can save money and trouble if internal skills are scarce
* How: Apply them wisely

[P7]
* When: In the introduction
* Who: Craig Larman
* What: Introduce, train certified Scrum masters

[P8]
* When: Earlier
* What: External consulting had been contracted
--
* When: In the transformation
* What: Used a wide range of external consultants

[P9]
* When: In the beginning
* Who: Ken Schwaber, Jeff Sutherland
* What: To ignite interest
--
* When: In the adaption
* Who: Experienced agile coaches
* What: To train Scrum on a regular basis

[P16]
* When: In the beginning
* Who: Industry experts
* What: The cross functional team reached out to consultants
--
* When: In the transformation
* Who: Professional trainers
* What: 25\% of R\&D sent to professional training 
* Who: Experienced consultants
* What: assist teams POs and ScMs
* Benefit: A key success factor
* Benefit: Their experience helped drive the transformation
* Benefit: People were more comfortable receiving advice from outsiders

[P17]
* Who: Rally software
* What: Provide software and services to accelerate adoption
* Benefit: Top notch consulting is critical for success

[P18]
* When: For the pilot team
* Who: Agile consultants
* What: A one day training, acting as a coach

[P19]
* When: In the beginning
* Who: Ken Schwaber
* What: Train 60 Scrum masters

[P20, P21]
* When: In the beginning
* Who: Expert agile consultant
* What: Assessment of the current process, educating management and agile task force
* What: Recommended to adopt Scrum
* What: Supervised the agile course held to initial team members

[P23]
* When: In the transformation, when looking for more coaches
* Who: Exoftware Ltd
* What: A partnership to promoting and coaching agile delivery

[P25]
* When: During the first year
* Who: External consultants
* What: Participate in the transformation team, support transformation of teams
--
* When: Later
* Who: Acclaimed agile professionals, external speakers
* What: Give presentations, lead workshops

[P27]
* When: In the beginning
* Who: Renowed industry experts, ThoughtWorks
* What: Educate employees on agile practices
--
* When: In the first couple of months
* What: Coaching the team
* Particular: The teams were sceptical of having external consultants embedded
--
* When: In the middle of the transformation
* Who: Agile consultants who were familiar with all phases of the transformation
* What: Workshops, coaching
* What: Enabled forward progress, avoided time wasted in searching solutions

[P29]
* When: Introducing Scrum to the department, later internal people took over
* What: coaching teams
* Particular: Good having an impartial third party to fall back on

[P30]
* When: In beginning, and through out
* Who: Jeff Sutherland
* What: Scrum training for most of the engineering group
* What: Sell the agile approach in the beginning
* Benefit: An outside expert sells the agile approach in the beginning
* It worked out with the external expert where there had been failures earlier

[P31]
* When: Teams had implemented agile, it was time to renew the requirements management
* Who: Enthiosys, management consulting company, with deep agile experience
* What: Help in creating a system to deliver end to end in an agile way

[P34]
* When: In the beginning
* Who: ThoughtWorks consulting company
* What: Support project management and development
* Why: Accelerate use of agile practices

[P35]
* Who: Agile contractors
* Why: To speed up the development

[P37, P38]
* When: In the beginning
* Who: A local consulting firm
* What: Assist with the transformation
[P38]
* Why: To give a shining example of agile
* What: Mentoring and helping teams

[P39]
* When: In the beginning
* Who: Two consulting companies
* What: Coach implementing agile

[P40]
* When: In the beginning, they moved out after three months
* Who: Consultants
* Why: The key projects were not to be affected, so people with previous
       knowledge were needed to create a roadmap
* Benefit: They moved quickly, as they had previous experience of similar transformations

[P41]
* When: In the beginning
* Who: known agile coaches
* What: Create a vision
* What: Help in developing and leading a transition workshop

[P43]
* When: In the beginning
* Who: Consultant firms
* What: Give initial insights, give insights during the transformation

[P44]
* When: In the beginning
* Who: Ken Schwaber
* What: Assess the current state
* What: Hold workshops, certify Scrum masters
* Benefit: Get impartial feedback from an outside source

[P46]
* When: In the beginning
* Who: Ken Schwaber
* What: Organizational coach
* Coach pilot teams in the beginning

[P47]
* When: in the beginning
* Who: External consultants
* What: Coach the apprentice coaches
* Particular: The need for the external coaches reduced over time, and gave way for internal
* Benefit: Support the early growth of apprentice coaches

[P50]
* Who: Consultants from Scrum foundation
* What: Coaching, training

[P51]
* When: In the beginning
* Who: External consultant
* What: Assess the current state, and recommend what to do
* What: Provide training

@@

\begin{table}[h]
    \centering
    \begin{tabular}{ >{\raggedright\arraybackslash}p{0.51\textwidth}
                     >{\raggedright\arraybackslash}p{0.41\textwidth} }
        \toprule
        Success factors  &  Described in \\
        \midrule
        Training is necessary to achieve change  &
                P3, P6, P11, P14, P16, P30, P37, P46 \\
        Coaching is essential in transformation  &
                P3, P6, P8, P9 P16, P17, P18, P29, P30, P33, P42, P44, P47, P48  \\
        \bottomrule
    \end{tabular}
    \caption{XXXXXXXXXXXXXX}
    \label{table:success_NN}
\end{table}

@@

Agile methods avoid prescribing exact ways of working but rather emphasize a
mindset of adapting to the situation. It is difficult to explain by theory how
such a mindset should be applied, and the agile practices are best learned by
doing. Coaching teams while they apply the agile methods in practice was seen as
an important factor in change [P3, P16, P17, P30, P47]. A few cases stated even
that coaching was essential for success in transformation [P8, P18, P29, P33].
Also, without coaching teams can do damage to the agile transformation if
techniques are applied improperly [P9].

@@

* It is difficult to distinguish between team and organization. In most cases
  when talking about teams it refers to a handfull of people familiar to each
  other. However, in some cases it was evident that an entire department was
  referred to as a team.

* Projects and organizations. How to distinguish between a separate adoption in
  the beginning of each project, and an organization wide adoption.
